---
title: "Alcohol vs Seat choice"
author: "Logan Kimbrough"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
 Showing from the results of the boxplot. The back seats have more than the front and middle.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```
  
Showing from the fancy box plot it looks like the back has the most alcohol.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

The front is different from the back. The back is drinking more then the people in the middle. The front is drinking more than the back and the middle.

## Conclusions

The challenge value is 5%, it is much smaller than .05 therefore the odds of getting something like this happens .000116 of the time.

